%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

% Software Engineer - Just Eat Takeaway
\cventry%
  {Software Engineer} % Job title
  {Just Eat Takeaway} % Company
  {Bristol, United Kingdom} % Location
  {09/2024--Present} % Date
  {
    \begin{cvitems}
      \item Engineered and architected a system which generated $\euro$243 million in revenue.
      \item Migrated legacy services from EC2 to Kubernetes, reducing operational costs by 30%.
      \item Brighter implementation, reduced duplicated code across all microservices.
      \item Created E2E tests and integrated them into our CI/CD pipelines to improve reliability of services.
      \item Championed initiatives to bring value to our product to improve agent and partner efficiency. (discounts/bulk upload)
      \item Mentored senior developers moving to .NET and provided guidance on best practices.
    \end{cvitems}
  }

%------------------------------------------------

% Software Consultant - Ensono
\cventry%
  {Software Consultant} % Job title
  {Ensono} % Company
  {Remote, United Kingdom} % Location
  {04/2022--07/2024} % Date
  {
    \begin{cvitems}
      \item Successfully delivered a microservices project for a specialty retailer in the UK, overhauling their buying and merchandising system. This $\pounds$5 million project involved cross-functional teams collaborating seamlessly.
      \item Utilized a robust CI/CD pipeline to ensure a reliable deployment to a Kubernetes cluster.
      \item Helped undertake a $\pounds$1.2 million venture to reconstruct the admissions and finance communications systems for a London-based university.
      \item This greenfield project built a microservices architecture exclusively utilizing Azure Functions and Azure Service Bus.
      \item Adopted a TDD approach, using automated testing, to deliver a stable product.
    \end{cvitems}
  }

%------------------------------------------------

% Backend Developer - Tytonical
\cventry%
  {Backend Developer} % Job title
  {Tytonical} % Company
  {Remote, United Kingdom} % Location
  {06/2020--04/2022} % Date
  {
    \begin{cvitems}
      \item Led end-to-end project development, including backend web APIs and full-stack applications.
      \item Researched, prioritizing scalability and high availability, and deployed applications on AWS ECS cluster.
      \item Fostered collaborations with partner companies, ensuring seamless integration.
      \item Guided a small group of interns as a team lead, teaching them programming skills through structured sessions and hands-on projects.
    \end{cvitems}
  }

%------------------------------------------------
  
% App Manager - Newpark Solutions
\cventry%
  {App Manager} % Job title
  {Newpark Solutions} % Company
  {Bristol, United Kingdom} % Location
  {01/2019--06/2020} % Date
  {
    \begin{cvitems}
      \item Launched a full redesign of the parking payment app.
      \item Led a small team, overseeing customer support and quality assurance departments.
      \item Maintained the backend web services while developing new functionality for incoming clients.
      \item Improved the app store rating from 1.5-2 to 4+.
    \end{cvitems}
  }

%------------------------------------------------
  
% Software Engineer - Newpark Solutions
\cventry%
  {Software Engineer} % Job title
  {Newpark Solutions} % Company
  {Bristol, United Kingdom} % Location
  {06/2018--01/2019} % Date
  {
    \begin{cvitems}
      \item Successfully integrated with a brand-new payment service provider for in-app payments.
      \item Built many new backend services, including an automated payment system that created an effortless parking experience.
      \item Collaborated closely with front-end developers to ensure seamless integration between backend services and mobile applications.
      \item Optimized database queries, resulting in a 20% reduction in response times for key API endpoints.
    \end{cvitems}
  }

%------------------------------------------------

\end{cventries}